Forecasting the 2024 US Presidential Election

### 2024-10-15 paper/paper.qmd
Updated data reference and data section in the paper.

## Overview
We use the statistical programming language R [@citeR] and utilize the "Presidential general election polls" dataset [@source].

>>>>

## Overview
We obtained the "Presidential general election polls" dataset from FiveThirtyEight [@FiveThirtyEight2024] and used the statistical programming language R [@citeR] to analyze this data.
